Probabilistic Inference of NYC Congestion from Taxi Data

### 2017-12-10 reports/paper/paper.tex
Add learned weight data, put unif map figure into paper.
Added softmax loss.
.
Clean up paper.

{\color{gray}\begin{itemize}
\item What were the results comparing previous work / baseline systems / your systems on the main task?
\item What were the secondary results comparing the variants of your system?
\item This section should be fact based and relatively dry. What happened, what was significant?
\end{itemize}
}

@@

% TODO fig

@@

% \begin{table}
%   \centering
%   \missingfigure[figheight=5cm]{}
%   \caption{Secondary table or figure in results section.}
%   \label{fig:mainres}
% \end{table}

@@

\begin{itemize}
\item What conclusions can you draw from the results section?
\item Is there further analysis you can do into the results of the system? Here is a good place to include visualizations, graphs, qualitative analysis of your results.

\item  What questions remain open? What did you think might work, but did not?
\end{itemize}

>>>>

% {\color{gray}\begin{itemize}
% \item What were the results comparing previous work / baseline systems / your systems on the main task?
% \item What were the secondary results comparing the variants of your system?
% \item This section should be fact based and relatively dry. What happened, what was significant?
% \end{itemize}
% }

@@

@@

@@

% \begin{itemize}
% \item What conclusions can you draw from the results section?
% \item Is there further analysis you can do into the results of the system? Here is a good place to include visualizations, graphs, qualitative analysis of your results.
% \item  What questions remain open? What did you think might work, but did not?
% \end{itemize}

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{figs/unifmaps.pdf}
\includegraphics[width=0.5\textwidth]{figs/softmaxmaps.pdf}
\caption{Learned Weights, Various Times Tuesday. Top Row: Uniform Model.
Bottom Row: Softmax Model.}
\label{fig:unifmap}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{figs/softmaxloss}
\caption{Softmax model training loss, rolling average.}
\label{fig:softmaxloss}
\end{figure}
